Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2022-05-31 manuscript.Rmd
try to load encoding

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: false
header-includes:
   - \usepackage{libertine}
fontsize: 11pt
linestretch: 1.2
geometry: "left=3.9cm, right=3.3cm, top=2.5cm, bottom=3cm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(readLines('abstract.md'), collapse = ' ')`"
---

@@

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(getOption("tikzXelatexPackages"), "\\usepackage{amsfonts}", "\\usepackage{libertine}")
)
```

@@

```{r, dev = "tikz", cache=TRUE}
results %>%
  mutate(name = str_remove(name, "Measure")) %>% 
  split(., .$name) %>%
  imap(
    ~ ggplot(.x, aes(enh, value)) +
      geom_line(aes(linetype = certainty)) + 
      labs(title = .x$name, y = element_blank(), x = element_blank())
  ) %>% 
  reduce(`+`) +
  plot_layout(ncol = 2, guides = 'collect') &
  theme_tufte() &
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(size = 7),
        axis.text = element_text(size = 6))
```

>>>>

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: false
    number_sections: false
header-includes:
   - \usepackage{libertine}
fontsize: 11pt
linestretch: 1.2
geometry: "left=3.9cm, right=3.3cm, top=2.5cm, bottom=3cm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(readLines('abstract.md'), collapse = ' ')`"
---

@@

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(
    getOption("tikzXelatexPackages"),
    "\\usepackage{amsfonts}",
    "\\usepackage[utf8]{inputenc}",
    "\\usepackage{libertine}"
  )
)
```

@@

```{r, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "Several measures for corroboration as increase in firmness as a function of α, where α is either certain (solid line) or maximally uncertain (dotted line)."

results %>%
  mutate(name = str_remove(name, "Measure")) %>%
  split(., .$name) %>%
  imap(
    ~ ggplot(.x, aes(enh, value)) +
      geom_line(aes(linetype = certainty)) +
      labs(
        title = .x$name,
        y = element_blank(),
        x = element_blank()
      )
  ) %>%
  reduce(`+`) +
  plot_layout(ncol = 2, guides = 'collect') &
  theme_tufte() &
  theme(
    legend.title = element_blank(),
    legend.position = "bottom",
    plot.title = element_text(size = 7),
    axis.text = element_text(size = 6)
  )
```
